data_cleaning_longer_period

### 2024-10-02 code/manuscript_altanalysis.Rmd
try again

```{r}
dfc <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
uds.sites.full <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>%
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))

@@

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  #filter(`2011` == 1 & `2012` == 1 ) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
  #filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2021`) %>% 
  pivot_longer(cols = c(`2010`:`2021`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  #filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

dfc <- dfc %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate + cad.rate + asthma.rate + ivd.rate ) / 9 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
            LiabPctAssets = Liabilities / Assets, 
            Eff = ngla_prog_serv_revenue / Assets, 
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense)

@@

table(table(dfc$`BHCMIS ID`))
```

@@

df.mt <- dfc %>% 
  left_join(df.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear")) %>% 
  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)), NA, log(Total / Staff))) %>% 
  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) / 
                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev)) %>% 
  mutate(dm.rate = dm.rate * 100, 
         htn.rate = htn.rate * 100, 
         pap.rate = pap.rate * 100, 
         crc.rate = crc.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         asthma.rate = asthma.rate * 100, 
         cad.rate = cad.rate * 100, 
         ivd.rate = ivd.rate * 100)
```

@@

df.temptemp <- df.mt %>% 
  rename(ID = ID.x) %>% 
  mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
  select(value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Complexity, Intensity, Pct.None:Pct.COM, CostPerPat, Altman) %>% 
  unique() %>% 
  filter(Year >= 2012)

@@

for (k in 1:(ncol(df.temptemp)-13)){

@@

}
data.frame(cbind(colnames(df.temptemp)[14:ncol(df.temptemp)], (coeffs[-1,])))

@@

```{r}
df.mt %>% 
  filter(Year >= 2012) %>% 
  mutate(value = ifelse(value > 6, 6, value)) %>% 
  group_by(value) %>% 
  summarise(n(), mean(MS, na.rm = TRUE), mean(Complexity, na.rm = TRUE))
```

>>>>

```{r}
dfc <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/analyticalfile.csv")
#uds.sites.full <- read_csv("/Users/markow/Dropbox/Git/Competition/data_processed/sites_geocoded.csv") %>%
#  mutate(Access = ifelse(`BHCMIS ID` == "080170" & as.numeric(`Total Weekly Hours Of Operation`) > 40000, 4, Access))
clinics.in.zips <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>%
  #filter(Year >= included.years[1]) %>%
  group_by(Zip, Year) %>%
  summarise(Clinics = n_distinct(`BHCMIS ID`), Sites = n()) %>%
  arrange(desc(Clinics))

@@

## Build List of ALL CHCs, star constructing variables
```{r}

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  #filter(`2011` == 1 & `2012` == 1 ) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
  #filter(`2010` == 1 & `2011` == 1 & `2012` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2023`) %>% 
  pivot_longer(cols = c(`2010`:`2023`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  #filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

dfc <- dfc %>% 
  mutate(Qcomp = (dm.rate + htn.rate + crc.rate + pap.rate + childbmi.rate + adultbmi.rate ) / 6 * 100, 
         Qcomp.w = (dm.rate * dm.total + htn.rate * htn.total + crc.rate * crc.denom + pap.rate * pap.denom + childbmi.rate * childbmi.denom + adultbmi.rate * adultbmi.denom ) / 
           ( dm.total +  htn.total +  crc.denom +  pap.denom +  childbmi.denom +  adultbmi.denom ) * 100, 
               CostPerPat = ngla_expense / Total, 
               months_of_cash = as.numeric(months_of_cash),
               ngla_prog_serv_revenue = as.numeric(ngla_prog_serv_revenue),
               quick_ratio = as.numeric(quick_ratio),
               Liquidity = (Assets - Liabilities) / Assets,
               Profitability = ngla_net_gain_loss / Assets, #Assets, 
               Efficiency = ngla_revenue / Assets, #ngla_revenue / Assets,
               NetWorth = (Assets - Liabilities) / Liabilities, 
            Pexpenses = ngla_prog_serv_revenue / ngla_prog_expense, 
            LiabPctAssets = Liabilities / Assets, 
            Eff = ngla_prog_serv_revenue / Assets, 
            LiabPctRev = ngla_prog_serv_revenue / ngla_expense)

@@

table(table(dfc$`BHCMIS ID`))

dfc %>% filter(ID.x == "90")
```

@@

df.mt <- dfc %>% 
  left_join(df.zip, by = c("BHCMIS ID" = "BHCMISID", "Year" = "ReportingYear")) %>% 
  mutate(logPatsPerStaff = ifelse(is.infinite(log(Total / Staff)), NA, log(Total / Staff))) %>% 
  mutate(Complexity = (HIV.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev) / 5, 
         Intensity = (HIV.care + HeartDisease.care + Depression.care + Diabetes.care + Hypertension.care) / 5, 
         Intensity.w = (HIV.care * HIV.prev + HepC.care * HepC.prev + Asthma.care * Asthma.prev + HeartDisease.care * HeartDisease.prev + Depression.care * Depression.prev + Diabetes.care * Diabetes.prev + Hypertension.care * Hypertension.prev) / 
                  (HIV.prev+ HepC.prev + Asthma.prev + HeartDisease.prev + Depression.prev + Diabetes.prev + Hypertension.prev)) %>% 
  mutate(dm.rate = dm.rate * 100, 
         htn.rate = htn.rate * 100, 
         pap.rate = pap.rate * 100, 
         crc.rate = crc.rate * 100, 
         childbmi.rate = childbmi.rate * 100, 
         adultbmi.rate = adultbmi.rate * 100, 
         asthma.rate = asthma.rate * 100, 
         cad.rate = cad.rate * 100, 
         ivd.rate = ivd.rate * 100)

@@

df.temptemp <- df.mt %>% 
  rename(ID = ID.x) %>% 
  mutate(Closed = ifelse(lead(is.na(Sites)), 1, 0)) %>% 
  select(value, ID, MS, Year, Pct.NHA:Pct.Homeless, Qcomp, Complexity, Intensity, Pct.None:Pct.COM, CostPerPat, Altman, Staff) %>% 
  unique()

df.temptemp <- df.temptemp %>% 
  group_by(ID) %>% 
  mutate(value_min = min(value, na.rm = TRUE), value_max = max(value, na.rm = TRUE), value_last = last(value, na_rm = TRUE), value_first = first(value, na_rm = TRUE)) %>% 
  mutate(Tx = value - value_min) %>% 
  filter(value_min == value_max | value_last > value_first)

@@

for (k in 1:10){

@@

}
data.frame(cbind(colnames(df.temptemp)[14:23], (coeffs[-1,])))

@@

## BY Hand
```{r}

df.temptemptemp <- df.temptemp %>% select(Qcomp, MS, value, Year, ID, Pct.NHA:Pct.COM) %>% ungroup() %>% filter(complete.cases(.))

reduced <- lm(data = df.temptemptemp, Qcomp ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )
firststage <- lm(data = df.temptemptemp, I(MS/10) ~ value + factor(Year) + factor(ID) + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless )

model <- lm(data = df.temptemptemp, Qcomp ~ firststage$fitted.values + Pct.NHB + Pct.HL + Pct.LessThan100pctFPL + Pct.FarmWorker + Pct.Homeless)
summary(model)

### 2024-10-02 code/manuscript_data_cleaning.Rmd
alt spec
more new analysis
try again

included.years <- 2010:2021
included.treat <- 2013:2019

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  #filter(`2011` == 1 & `2012` == 1 ) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
  filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2023`) %>% 
  pivot_longer(cols = c(`2014`:`2023`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

vec.atts <- rep(included.treat, (table(comp.initial$Att) / 12)[-1])

>>>>

@@

# Identify clinics in competitive zip codes
clinics.comp <- uds.sites.full[!is.na(uds.sites.full$Zip),] %>% 
  filter(Year >= included.years[1]) %>%
  select(`BHCMIS ID`, Zip, Year) %>% 
  unique() %>% 
  left_join(clinics.in.zips, by = c("Zip", "Year")) %>% 
  group_by(`BHCMIS ID`, Year) %>% 
  summarise(Clinics = max(Clinics)) %>% 
  pivot_wider(id_cols = `BHCMIS ID`, names_from = Year, values_from = Clinics) %>% 
  #filter(`2011` == 1 & `2012` == 1 ) %>%  #  & `2012` == 1 & `2013` == 1 & `2014` == 1 & `2015` == 1 & `2016` == 1) %>%   
  #filter(`2014` == 1 & `2015` == 1) %>%  
  #left_join(chc.term, by = c("BHCMIS ID" = "ClinicID")) %>%
  #filter(is.na(NewClinicID)) %>%
  select(`BHCMIS ID`:`2023`) %>% 
  pivot_longer(cols = c(`2010`:`2023`)) %>% 
  group_by(`BHCMIS ID`) %>% 
  filter(min(value) == 1 ) %>% 
  #filter(max(value) == last(value)) %>% 
  mutate(Tx = ifelse(value > 1, 1, 0))

@@

#vec.atts <- rep(included.treat, (table(comp.initial$Att) / 15)[-1])
vec.atts <- included.treat
